---
title: "Discharge Monitoring"
author: ""
date: "10 December 2018"
output: html_document
---


```{r setup, include=FALSE}
library(sepaTools) # to get SEPA data
library(dplyr) # for data manipulation
library(broom) # tidy model outputs
library(DT) # nice html tables
knitr::opts_chunk$set(echo = F, comment = F, warning = F, message = F) # some option for presentations of html
```

## Samples 

List of tests per site per season. Up and downstream results only (excluding tributaries for now). This is to help spot missing samples:

```{r}
filePath <- "data/locations.csv"
locations <- read.csv(file = filePath) 
locations <- filter(locations, SUITABILITY == "yes")
  
results <-  getEcologyResults(locations = locations$LOCATION_CODE,
                               analysis = c("F_BMWP_TST",
                                            "F_BMWP_SUM",
                                            "SEW_FUNGUS",
                                            "SURVEY_INV"),
                               startDate = "01-MARCH-2018",
                               endDate = "01-NOV-2018")

 
results <-  inner_join(locations, results,by = "LOCATION_CODE")
results$DATE <- as.Date(results$DATE_TAKEN, "%d/%m/%y")

# filter and summarize up and downstream results only (not tribs)
result <- filter(results, POSITION %in% c("DS","US"))
result <- group_by(result, STW, SEASON, ANALYSIS, DETERMINAND) %>% mutate(COUNT = n())
result <- ungroup(result)

result_sum <- group_by(result, LOCATION_CODE, LOCATION_DESCRIPTION.x, STW, SEASON, ANALYSIS_REPNAME) %>%
  summarize(COUNT = length(unique(TEST_NUMBER))) 
  DT::datatable(result_sum,rownames = F)

```

## T-tests

Run pair-wise t-test for all samples. The 'pair' is defined as a sample taken up and downstream of a single Waste Water Treatment Works (WWTW) within the same season. Where multiple reps have been taken within a season, they are paired based on time/date.

The Null hypothesis is that WHPT scores are great downstream than upstream. 


```{r t-tests}

# arrange by date taken so reps are pair-wised match on date/time taken.
result <- arrange(result, DATE_TAKEN)

t_test <- lapply(split(result, result$STW), function(result) {
 t_test <- lapply(c("WHPT NTAXA Abund","WHPT ASPT Abund"), function(WHPT) {
    
 
  upstream = result$VALUE[result$DETERMINAND == WHPT &
  result$POSITION == "US" &
  result$COUNT %in% c(2, 8)]

  downstream = result$VALUE[result$DETERMINAND == WHPT &
  result$POSITION == "DS" &
  result$COUNT %in% c(2, 8)]

  test <- NULL
  try(t_test <- t.test(downstream, 
                     upstream, 
                     var.equal = TRUE, 
                     paired = T, 
                     alternative = "l"))
  try(test <- tidy(t_test))
  test$STW <- unique(result$STW)
  test$TYPE <- WHPT

  return(test)
})
   return(bind_rows(t_test))
})
all <- bind_rows(t_test)
all <- select(all, STW, TYPE, everything())
DT::datatable(all ,rownames = F)

```

